cardinalR: Generating interesting high-dimensional data structures

### 2025-09-16 paper-cardinalR.Rmd
Updated the operations ordering of Mobius fuctions
Added descriptions for theta and w in Mobius

The Mobius strip is generated using the `geozoo::mobius` function with `p = 3`, and `n` defined as above. This function samples $n$ points from a parameterization of the surface defined by angle $\theta$ and strip width $w$. The cartesian coordinates are $X_1 = \left(1 + w/2 \cos(\theta/2)\right) \cos(\theta)$, $X_2 = \left(1 + w/2 \cos(\theta/2)\right) \sin(\theta)$, and $X_3 = w/2 \sin(\theta/2)$. This maps a $2\text{-}D$ band with a half-twist into $3\text{-}D$ space, forming a non-orientable one-sided surface. For $p > 3$, Gaussian noise $X_j \sim N(0, 0.05^2)$ is added to embed the $3\text{-}D$ Mobius into $p\text{-}D$, where $j = 4, \dots, p$.

>>>>

The Mobius strip is generated using the `geozoo::mobius` function with `p = 3`, and `n` defined as above. Each point is sampled from a parameterization defined by an angle $\theta \sim U(0, 2\pi)$, which specifies the position along the circular loop, and a width $w \sim U(-0.4, 0.4)$, which offsets the point across the strip’s band. The cartesian coordinates are $X_1 = \left(1 + (w/2) \cos(\theta/2)\right) \cos(\theta)$, $X_2 = \left(1 + (w/2) \cos(\theta/2)\right) \sin(\theta)$, and $X_3 = (w/2)\sin(\theta/2)$. This maps a $2\text{-}D$ band with a half-twist into $3\text{-}D$ space, forming a non-orientable one-sided surface. For $p > 3$, Gaussian noise $X_j \sim N(0, 0.05^2)$ is added to embed the $3\text{-}D$ Mobius into $p\text{-}D$, where $j = 4, \dots, p$.

### 2025-09-16 paper-cardinalR.tex
Updated the operations ordering of Mobius fuctions
Added descriptions for theta and w in Mobius

The Mobius strip is generated using the \texttt{geozoo::mobius} function with \texttt{p\ =\ 3}, and \texttt{n} defined as above. This function samples \(n\) points from a parameterization of the surface defined by angle \(\theta\) and strip width \(w\). The cartesian coordinates are \(X_1 = \left(1 + w/2 \cos(\theta/2)\right) \cos(\theta)\), \(X_2 = \left(1 + w/2 \cos(\theta/2)\right) \sin(\theta)\), and \(X_3 = w/2 \sin(\theta/2)\). This maps a \(2\text{-}D\) band with a half-twist into \(3\text{-}D\) space, forming a non-orientable one-sided surface. For \(p > 3\), Gaussian noise \(X_j \sim N(0, 0.05^2)\) is added to embed the \(3\text{-}D\) Mobius into \(p\text{-}D\), where \(j = 4, \dots, p\).

>>>>

The Mobius strip is generated using the \texttt{geozoo::mobius} function with \texttt{p\ =\ 3}, and \texttt{n} defined as above. Each point is sampled from a parameterization defined by an angle \(\theta \sim U(0, 2\pi)\), which specifies the position along the circular loop, and a width \(w \sim U(-0.4, 0.4)\), which offsets the point across the strip's band. The cartesian coordinates are \(X_1 = \left(1 + (w/2) \cos(\theta/2)\right) \cos(\theta)\), \(X_2 = \left(1 + (w/2) \cos(\theta/2)\right) \sin(\theta)\), and \(X_3 = (w/2)\sin(\theta/2)\). This maps a \(2\text{-}D\) band with a half-twist into \(3\text{-}D\) space, forming a non-orientable one-sided surface. For \(p > 3\), Gaussian noise \(X_j \sim N(0, 0.05^2)\) is added to embed the \(3\text{-}D\) Mobius into \(p\text{-}D\), where \(j = 4, \dots, p\).
